\\textsc{Mathematical Description}

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Implement new math operators

* For simplicity, we use the term "adult" to refer to any mature individual returning to spawn -- this includes age-3 fish which are generally referred to as "jacks".
* Life stage-specific states are defined by capital letters, e.g., parr ($P$), smolt ($M$), or spawners ($S$)
* Parameters (e.g., survival terms, non-survival transition probabilities, coefficients in relationships, etc.) are denoted by Greek symbols, e.g., $\phi$ for survival rates or $\psi$ for maturation rates.
* Subscripts denote the structure of a quantity, e.g., $y$ denotes a specific year and $j$ a specific population.
* We use the convention $b$ to indicate "before event" and $a$ to indicate "after event" for a quantity that occurs at the same life stage. E.g., $M^{b}$ represents smolt abundance _before_ out-of-basin migration and $M^{a}$ represents smolt abundance _after_ out-of-basin migration. As such, superscripts are most often used syntactically, not mathematically. E.g., $M^{b}$ is not "$M$ raised to the power $b$"; if we must raise the quantity $M^{b}$ to the power $c$, it will be written $(M^{b})^c$.
* Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \rightarrow B}_{y,j}$.
* Most terms vary annually to capture process noise in population dynamics. We denote the deterministic (i.e., expected) value in the absence of process noise with a dot, e.g., $\dot{\phi}^{A \rightarrow B}_j$. We use the term "deterministic" in the sense that it is the expected value for a stochastic (i.e., with process noise) quantity; the deterministic quantity still has a posterior probability density function.
* In some cases, we specify calculations performed on vectors rather than scalars (i.e., a scalar being a single element from a vector or higher-dimensional array). Vectors are denoted via boldface, and the dimension of the vector is denoted using 1:$n$ syntax. E.g., $\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for a given population.
* Mathematical operations performed on two vectors $\boldsymbol{C}$ and $\boldsymbol{D}$ are performed in an element-wise fashion, and the resulting vector will have identical dimensions to both $\boldsymbol{C}$ and $\boldsymbol{D}$.
* In some cases, a calculation is performed differently for a subset of the possible index values. For example, to denote that $k$ should take on only the values of 1 and 3 (not 2), we would write, $k \in [1,3]$.
* $\log(x)$ represents the natural logarithm of $x$ (i.e., $\log_e(x)$) and it is implied that the constraint $x > 0$ is satisfied.
* $\logit(p)$ represents the log odds of $p$ (i.e., $\log[p/(1-p)])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
* All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \rightarrow B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \rightarrow B}_{y,j}}$, which we use as a direct estimate of observation error variability).
* Stochastic processes are represented by $x_{y} \sim \mathcal{F}(\theta_{1}, \theta_{2})$, where $x_{y}$ is a random variable, $\mathcal{F}$ is some probability density (or mass) function ($\mathcal{N}$ is univariate normal, $\mathcal{MVN}$ is multivariate normal, $\mathcal{B}$ is binomial, and $\mathcal{M}$ is multinomial), and $\theta_{1}$ and $\theta_{2}$ are parameters of the probability distribution; generally $\theta_{1}$ is a location parameter specifying the expected value of $x_{y}$ and $\theta_{2}$ is a dispersion parameter specifying the variability of $x_{y}$ around the expected value.

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
(\#eq:generic-random)
\end{equation}

@@

\begin{equation}
\log(\beta_j) \sim \mathcal{N}\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
(\#eq:beta-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
(\#eq:phi-E-Pb-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
(\#eq:pi-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
(\#eq:phi-Pa-Mb-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
(\#eq:phi-Ma-O0-random)
\end{equation}

@@

\begin{equation}
\log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
(\#eq:fall-count-data)
\end{equation}

@@

\begin{equation}
\log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
(\#eq:spring-count-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \mathcal{N}\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
(\#eq:summer-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
(\#eq:fall-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \mathcal{N}\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
(\#eq:winter-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
(\#eq:spring-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
(\#eq:spring-surv-HOR-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \mathcal{N}\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
(\#eq:hydro-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
(\#eq:phi-O0-O1-random)
\end{equation}

@@

\begin{equation}
\begin{aligned}
\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}_o}\right] \\
\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}_o}\right]
\end{aligned}
(\#eq:psi-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{R^{b} \rightarrow R^{a}}_{y,1:n_o}\right)
\begin{cases}
= \logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right) & \mbox{if $y < 10$}\\
\sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \rightarrow R^{a}}} \right] & \mbox{if $y \ge 10$}
\end{cases}
(\#eq:phi-Rb-Ra-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \mathcal{MVN}\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
(\#eq:phi-Sb-Sa-random)
\end{equation}

@@

\begin{equation}
\log\left(\hat{R}^{a}_{y,j}\right) \sim \mathcal{N}\left[\log\left(\sum_o^{n_o} \sum_k^{n_k} R^{a}_{y,k,o,j}\right), \hat{\sigma}_{R^{a}_{y,j}}\right]
(\#eq:Ra-data)
\end{equation}

@@

\begin{equation}
\hat{x}^{\mathrm{LGR}}_{y,o} \sim \mathcal{B}\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
(\#eq:upstream-surv-data)
\end{equation}

@@

\begin{equation}
\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \mathcal{B}\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
(\#eq:prespawn-surv-data)
\end{equation}

@@

\begin{equation}
\boldsymbol{\hat{x}}^{R^{a}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{R^{a}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}\right)
(\#eq:weir-comp-data)
\end{equation}

@@

\begin{equation}
z_{k,j} \sim \mathcal{N}(\dot{z}_{k}, \sigma_{z_k})
(\#eq:z-random)
\end{equation}

@@

\begin{equation}
\log(\zeta_{k,j}) = z_{k=1,j} \cdot \mathrm{age3}_k + z_{k=3,j} \cdot \mathrm{age5}_k
(\#eq:get-zeta-no-minam)
\end{equation}

@@

\begin{equation}
\boldsymbol{\hat{x}}^{S^{a^{\prime}}}_{y,1:n_{ko},j} \sim \mathcal{M}\left(\boldsymbol{p}^{S^{a^{\prime}}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{S^{a^{\prime}}}_{y,ko,j}\right)
(\#eq:carcass-comp-data)
\end{equation}

>>>>

* For simplicity, we use the term "adult" to refer to any mature individual returning to spawn -- this includes age-3 fish which are generally referred to as "jacks".
* Life stage-specific states are defined by capital letters, e.g., parr ($P$), smolt ($M$), or spawners ($S$)
* Parameters (e.g., survival terms, non-survival transition probabilities, coefficients in relationships, etc.) are denoted by Greek symbols, e.g., $\phi$ for survival rates or $\psi$ for maturation rates.
* Subscripts denote the structure of a quantity, e.g., $y$ denotes a specific year and $j$ a specific population.
* We use the convention $b$ to indicate "before event" and $a$ to indicate "after event" for a quantity that occurs at the same life stage. E.g., $M^{b}$ represents smolt abundance _before_ out-of-basin migration and $M^{a}$ represents smolt abundance _after_ out-of-basin migration. As such, superscripts are most often used syntactically, not mathematically. E.g., $M^{b}$ is not "$M$ raised to the power $b$"; if we must raise the quantity $M^{b}$ to the power $c$, it will be written $(M^{b})^c$.
* Survival terms to transition from state $A$ to state $B$ in year $y$ for population $j$ are denoted by $\phi^{A \rightarrow B}_{y,j}$.
* Most terms vary annually to capture process noise in population dynamics. We denote the deterministic (i.e., expected) value in the absence of process noise with a dot, e.g., $\dot{\phi}^{A \rightarrow B}_j$. We use the term "deterministic" in the sense that it is the expected value for a stochastic (i.e., with process noise) quantity; the deterministic quantity still has a posterior probability density function.
* In some cases, we specify calculations performed on vectors rather than scalars (i.e., a scalar being a single element from a vector or higher-dimensional array). Vectors are denoted via boldface, and the dimension of the vector is denoted using 1:$n$ syntax. E.g., $\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}$ represents a vector of survival terms from state $A$ to state $B$ in year $y$, where each element of the vector represents the value for a given population.
* Mathematical operations performed on two vectors $\boldsymbol{C}$ and $\boldsymbol{D}$ are performed in an element-wise fashion, and the resulting vector will have identical dimensions to both $\boldsymbol{C}$ and $\boldsymbol{D}$.
* In some cases, a calculation is performed differently for a subset of the possible index values. For example, to denote that $k$ should take on only the values of 1 and 3 (not 2), we would write, $k \in [1,3]$.
* $\log\left(x\right)$ represents the natural logarithm of $x$ and it is implied that the constraint $x > 0$ is satisfied.
* $\logit\left(p\right)$ represents the log odds of $p$ (i.e., $\log\left[p/(1-p)\right])$) and it is implied that the constraint $0 < p < 1$ is satisfied.
* All quantities that have been empirically observed (or externally estimated from empirically observed data, and supplied to the model as "data") and are used in a likelihood component are denoted by a "hat", e.g., a survival term ($\hat{\phi}^{A \rightarrow B}_{y,j}$) and its logit-normal standard error ($\hat{\sigma}_{\phi^{A \rightarrow B}_{y,j}}$, which we use as a direct estimate of observation error variability).
* Stochastic processes are represented by $x_{y} \sim \mathcal{F}(\theta_{1}, \theta_{2})$, where $x_{y}$ is a random variable, $\mathcal{F}$ is some probability density (or mass) function ($\mathcal{N}$ is univariate normal, $\mathcal{MVN}$ is multivariate normal, $\mathcal{B}$ is binomial, and $\mathcal{M}$ is multinomial), and $\theta_{1}$ and $\theta_{2}$ are parameters of the probability distribution; generally $\theta_{1}$ is a location parameter specifying the expected value of $x_{y}$ and $\theta_{2}$ is a dispersion parameter specifying the variability of $x_{y}$ around the expected value.

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{A \rightarrow B}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{A \rightarrow B}_{y,1:n_j}\right), \Sigma_{\phi^{A \rightarrow B}} \right]
(\#eq:generic-random)
\end{equation}

@@

\begin{equation}
\log\left(\beta_j\right) \sim \Ndist\left[\log\left(\lambda \cdot \mathrm{WUL}_j\right), \sigma_{\beta} \right]
(\#eq:beta-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{E \rightarrow P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{E \rightarrow P^{b}}_{y,1:n_j}\right), \Sigma_{\phi^{E \rightarrow P^{b}}}\right]
(\#eq:phi-E-Pb-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\pi}_{y,i = \mathrm{fall},1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\pi}}_{i = \mathrm{fall},1:n_j}\right), \Sigma_{\pi_{i = \mathrm{fall}}}\right]
(\#eq:pi-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{P^{a} \rightarrow M^{b}}_{y,i,1:n_j}\right), \Sigma_{\phi^{P^{a} \rightarrow M^{b}}_i}\right]
(\#eq:phi-Pa-Mb-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{M^{a} \rightarrow O^{0}}_{y,1:n_o}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{M^{a} \rightarrow O^{0}}_{1:n_o}\right), \Sigma_{\phi^{M^{a} \rightarrow O^{0}}}\right]
(\#eq:phi-Ma-O0-random)
\end{equation}

@@

\begin{equation}
\log\left(\hat{P}^{a}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\log\left(P^{a}_{y,i=\mathrm{fall},j} \right), \hat{\sigma}_{P^{a}_{y,i=\mathrm{fall},j}}\right]
(\#eq:fall-count-data)
\end{equation}

@@

\begin{equation}
\log\left(\hat{M}^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\log\left(M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right), \hat{\sigma}_{M^{b}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
(\#eq:spring-count-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{P^{b} \rightarrow M^{a}}_{y,j}\right) \sim \Ndist\left[\logit\left(\frac{\sum_{i}^{n_i} M^{a}_{y,i,o=\mathrm{NOR},j}}{P^{b}_{y,j}}\right),\hat{\sigma}_{\phi^{P^{b} \rightarrow M^{a}}_{y,j}}\right]
(\#eq:summer-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{fall},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{fall},j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{fall},j}}\right]
(\#eq:fall-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}\right) \sim \Ndist\left[\logit\left(\frac{M^{a}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}{P^{a}_{y,i=\mathrm{spring},j} \cdot \phi^{P^{b} \rightarrow P^{a}}_{j}}\right),\hat{\sigma}_{\phi^{P^{a} \rightarrow M^{a}}_{y,i=\mathrm{spring},j}}\right]
(\#eq:winter-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{NOR},j}}\right]
(\#eq:spring-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right) \sim \Ndist\left[\logit\left(\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}\right),\hat{\sigma}_{\phi^{M^{b} \rightarrow M^{a}}_{y,i=\mathrm{spring},o=\mathrm{HOR},j}}\right]
(\#eq:spring-surv-HOR-data)
\end{equation}

@@

\begin{equation}
\logit\left(\hat{\phi}^{M^{a} \rightarrow O^{0}}_{y,o}\right) \sim \Ndist\left[\logit\left(\phi^{M^{a} \rightarrow O^{0}}_{y,o}\right),\hat{\sigma}_{\phi^{M^{a} \rightarrow O^{0}}_{y,o}}\right]
(\#eq:hydro-surv-data)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left\{\logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right) + \boldsymbol{\kappa}^{O^{0} \rightarrow O^{1}}_{1:n_j} \cdot \left[ \logit\left(\boldsymbol{\phi}^{O^{0} \rightarrow O^{1}}_{y-1,o,1:n_j}\right) - \logit\left(\boldsymbol{\dot{\phi}}^{O^{0} \rightarrow O^{1}}_{o,1:n_j}\right)\right], \Sigma_{\phi^{O^{0} \rightarrow O^{1}}} \right\}
(\#eq:phi-O0-O1-random)
\end{equation}

@@

\begin{equation}
\begin{aligned}
\logit\left(\boldsymbol{\psi}^{O^{1}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{1}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{1}}_o}\right] \\
\logit\left(\boldsymbol{\psi}^{O^{2}}_{y,o,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\psi}}^{O^{2}}_{o,1:n_j}\right), \Sigma_{\psi^{O^{2}}_o}\right]
\end{aligned}
(\#eq:psi-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{R^{b} \rightarrow R^{a}}_{y,1:n_o}\right)
\begin{cases}
= \logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right) & \mbox{if $y < 10$}\\
\sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{R^{b} \rightarrow R^{a}}_{1:n_o}\right), \Sigma_{\phi^{R^{b} \rightarrow R^{a}}} \right] & \mbox{if $y \ge 10$}
\end{cases}
(\#eq:phi-Rb-Ra-random)
\end{equation}

@@

\begin{equation}
\logit\left(\boldsymbol{\phi}^{S^{b} \rightarrow S^{a}}_{y,1:n_j}\right) \sim \MVNdist\left[\logit\left(\boldsymbol{\dot{\phi}}^{S^{b} \rightarrow S^{a}}_{1:n_j}\right), \Sigma_{\phi^{S^{b} \rightarrow S^{a}}}\right]
(\#eq:phi-Sb-Sa-random)
\end{equation}

@@

\begin{equation}
\log\left(\hat{R}^{a}_{y,j}\right) \sim \Ndist\left[\log\left(\sum_o^{n_o} \sum_k^{n_k} R^{a}_{y,k,o,j}\right), \hat{\sigma}_{R^{a}_{y,j}}\right]
(\#eq:Ra-data)
\end{equation}

@@

\begin{equation}
\hat{x}^{\mathrm{LGR}}_{y,o} \sim \Bdist\left(\phi^{R^{b} \rightarrow R^{a}}_{y,o}, \hat{x}^{\mathrm{BON}}_{y,o}\right)
(\#eq:upstream-surv-data)
\end{equation}

@@

\begin{equation}
\hat{x}^{\mathrm{carcass,spawned}}_{y,j} \sim \Bdist\left(\phi^{S^{b} \rightarrow S^{a}}_{y,j}, \hat{x}^{\mathrm{carcass,total}}_{y,j}\right)
(\#eq:prespawn-surv-data)
\end{equation}

@@

\begin{equation}
\boldsymbol{\hat{x}}^{R^{a}}_{y,1:n_{ko},j} \sim \Mdist\left(\boldsymbol{p}^{R^{a}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{R^{a}}_{y,ko,j}\right)
(\#eq:weir-comp-data)
\end{equation}

@@

\begin{equation}
z_{k,j} \sim \Ndist(\dot{z}_{k}, \sigma_{z_k})
(\#eq:z-random)
\end{equation}

@@

\begin{equation}
\log\left(\zeta_{k,j}\right) = z_{k=1,j} \cdot \mathrm{age3}_k + z_{k=3,j} \cdot \mathrm{age5}_k
(\#eq:get-zeta-no-minam)
\end{equation}

@@

\begin{equation}
\boldsymbol{\hat{x}}^{S^{a^{\prime}}}_{y,1:n_{ko},j} \sim \Mdist\left(\boldsymbol{p}^{S^{a^{\prime}}}_{y,1:n_{ko},j}, \sum_{ko}^{n_{ko}} \hat{x}^{S^{a^{\prime}}}_{y,ko,j}\right)
(\#eq:carcass-comp-data)
\end{equation}
